Redesign the weekly calendar day-selector component for a beauty salon scheduling app (Portuguese BR). 
The component shows 7 days (SEG to DOM) in a horizontal row.

APPOINTMENT COLOR RULES (must be reflected in day cards):
- Purple #6C3FDB = Confirmed appointment
- Yellow/Amber #F5A623 = Waiting/Pending
- Green #2ECC71 = Present/Attended  
- Red #E74C3C = Cancelled

DESIGN REQUIREMENTS FOR EACH DAY CARD:

1. **Base card**: Rounded pill or tall rounded rectangle. Background lavender #EDE8FB. 
   Size: ~48px wide, 90px tall.

2. **Day abbreviation**: Top, small caps, muted color (e.g. #9B8EC4), 10px.

3. **Day number**: Center, bold, large (22px), dark #2D1B69.

4. **Appointment indicator area** (bottom of card):
   - If 0 appointments: empty / faint dash
   - If 1 appointment: show 1 colored dot (color = appointment status)
   - If 2+ appointments: show stacked small colored dots OR a mini 
     segmented bar with each appointment's status color
   - Max show 3 dots, then "+N" badge if more

5. **Selected day state**: 
   - Full purple background #6C3FDB
   - White text for abbreviation and number
   - Dots become white-outlined colored fills
   - Subtle drop shadow: 0 8px 20px rgba(108,63,219,0.35)
   - Slight scale up: 1.05x

6. **Today indicator**: 
   - Small white underline dot below the number (even when not selected)

7. **Spacing**: 6px gap between cards. Cards have 10px horizontal padding inside.

8. **Animation**: Selected card smoothly transitions with 200ms ease.

EXAMPLE STATE TO RENDER:
- SEG 11: 0 appts (empty)
- TER 12: 0 appts (empty)
- QUA 13: 0 appts (empty)
- QUI 14: 1 appt CONFIRMED (1 purple dot) — selected state
- SEX 15: 2 appts — 1 CANCELLED (red dot) + 1 WAITING (yellow dot) — today
- SÁB 16: 0 appts
- DOM 17: 0 appts

Color palette: primary #6C3FDB, bg #EDE8FB, today accent #F5A623, 
confirmed #6C3FDB, waiting #F5A623, present #2ECC71, cancelled #E74C3C.

Output: mobile component 375px wide, horizontal scroll if needed, 
pixel-perfect spacing, no text labels for appointment count — 
use ONLY colored dots/bars.